A Quality-of-Content (QoC)-based Joint Source and Channel Coding for Human Detections in A Mobile Surveillance Cloud

### 2015-08-14 draft.tex
First submitted version

\everymath{\displaystyle}
\newcommand{\tab}[1]{\hspace{.02\textwidth}\rlap{#1}}
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Quality-of-Content (QoC)-Based Wireless Video Transmissions: A Joint Source Coding and APP-FEC Rate Allocation Scheme for Human Detections in Mobile Surveillance Networks}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Xiang Chen, Jenq-Neng Hwang, Kuan-Hui Lee, Ricardo L. de Queiroz}   \\
\thanks{This study is partially supported by the “103-EC-17-A-03-S1-214” project from the Ministry of Economic Affairs (MOEA) of Taiwan and “Advanced Wireless Broadband System and Inter-networking Application Technology Development Project” of the Institute for Information Industry which is subsidized by the Ministry of Economy Affairs of Taiwan.}
\thanks{Xiang Chen is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: xchen28@uw.edu).}% <-this % stops a space
\thanks{Jenq-Neng Hwang is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: hwang@uw.edu).}% <-this % stops a space
\thanks{Kuan-Hui Lee is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: ykhlee@uw.edu).}
\thanks{Ricardo L. de Queiroz is with the Department
of Computer Science, Universidade de Brasilia, Brasilia, Brazil (e-mail: queiroz@ieee.org).}

@@

\begin{abstract}
%\boldmath
More than 70 percent of all the consumer mobile Internet traffic will be mobile video transmissions in 2019. The development of wireless video transmission technologies have been boosted by the rapidly increasing demand of video streaming applications. Although more and more videos are delivered for video analytics purposes (e.g., object detection/tracking and action recognition, etc.), however, most of existing wireless video transmission schemes are developed to optimize human perception qualities, which are no longer optimal for video analyses.  In mobile surveillance networks, a cloud server collects videos from multiple moving cameras and detects suspicious people in all the camera views. Due to the mobility of the moving cameras such as smartphone or dash cameras, videos have to be uploaded through bandwidth-limited and error-prone wireless networks, which may cause quality degradation of the decoded videos and jeopardize the performance of video analyses. In this paper, we propose an effective rate allocation scheme for multiple moving cameras so that the human detection (content) performance can be improved. Therefore, the optimization criterion of the proposed rate allocation scheme is driven by quality-of-content (QoC). Both video source coding and application layer forward error correction (APP-FEC) coding rates are jointly optimized. Moreover, the proposed rate allocation problem is formulated as a convex optimization problem and can be efficiently solved by standard solvers. Plenty of simulations with the high efficient video coding (HEVC) encoded video sequences and the deformable part model (DPM) object detector demonstrate the effectiveness and favorable performance of our proposed scheme under different pedestrain densities and wireless conditions.

@@

The exponentially increasing demand of video streaming services has boosted the developement of wireless video transmission technologies \cite{Hwan09}. In most of the existing studies, the optimization targets for wireless video delivery are either quality-of-service (QoS) \cite{Hwan09,EhHa12,KPKG15} or quality-of-experience (QoE) \cite{CHLC15,CHWL14,CDHR15,SHJE13,YaFA15}. For QoS-based design, the transmission scheme is optimized for network parameters such as packet loss rate, delay, jitter, etc. For QoE-based design, QoS measurements are mapped to users' perception and experience of decoded videos so that video transmission parameters can be adjusted to improve users' satisfaction \cite{FiHT10}. Both subjective and objective video quality measurements can be applied to quantify the QoE-based system design \cite{MSSB10}.

The Internet of Things (IoT) becomes a novel paradigm in modern wireless telecommunications \cite{AtIM10}. And video-based IoT, which integrates image processing, computer vision and network frameworks, will help develop a new challenging scientific research area at the intersection of video and network technologies \cite{GBMP13}. Such research areas include surveillance system, automatic behavior analysis and event detection, etc. \cite{GBMP13}. In fact, more and more videos are transmitted for video analytics purposes rather than human perceptions. In \cite{LeHC15}, a vehicle tracking system with static surveillance cameras is developed. In \cite{ChHw14}, an unsupervised learning of camera link models for tracking humans across nonoverlapping static cameras is invented. Based on human detectors, pedestrian tracking systems in single moving cameras are proposed \cite{LHOP14,HWLH15}. A system of on-road pedestrian tracking across multiple moving cameras is studied in \cite{LeHw15}. Due to the large computational cost of video analyses applications and the inter-cooperating properties between multiple cameras, videos are required to be uploaded to a cloud server through wired and/or wireless networks. However, transmitting videos based on QoS or QoE based on existing designs are no longer optimal if the videos are delivered for video analyses. Therefore, it is necessary to develope more efficient video transmission schemes specifically for video analysis and computer vision applications.

Mobile surveillance networks with multiple moving cameras, which have more flexible camera views comparing to traditional surveillance systems with static closed circuit television (CCTV), is introduced for better crime investigation and tragedy prevention \cite{LeHw15}. In mobile surveillance systems, videos are recorded by driving recorders (dash cameras) or smartphone cameras, and uploaded to remote cloud servers for further automatic video analyses. Due to the mobility nature of moving cameras, wireless wide area networks (WWAN) have to be used for video transmissions. Therefore, efficient video compression, error protection and resource allocation are needed because of the bandwidth-limited and the error-prone nature of wireless networks.

In mobile surveillance networks, in order to recognize and track suspicious people, several video analysis technologies need to be applied such as human detection, human tracking, action recognition, behavior understanding, etc.. Among these technologies, human detection is the first step and the performances of other human-related video analysis applications are critically affected by the human detection results \cite{LeHw15}. Although plenty of work has been conducted to improve the object detector in computer vision field \cite{DaTr05,LeLS08,FGMR10}, few studies can be found in wireless video transmission area when the performance degradations caused by video compression, wireless transmission errors are considered. In \cite{MiBR13}, a saliency-based rate control system for human detection with a single camera is proposed. To improve the human detection accuracy, this scheme adaptively adjusts the quantization parameters (QPs) to preserve regions with small contrast from excessive smoothing based on a properly designed saliency map. In \cite{CHLQ15}, we proposed a video srouce encoding rate allocation scheme when multiple moving cameras compete for a limited amount of wireless resource. This scheme adequately allocate the wireless resource to each moving camera based on its previous human detection results (contents). Since the optimization objective is to improve human detection performance, this scheme is called a quality-of-content (QoC)-based design.

In this paper, we extend our previous work in \cite{CHLQ15} by considering packet losses in wireless networks. Among several techniques of improving the reliability of data transmissions, we adopte the application layer forward error correction (APP-FEC) code since it can provide certain correction capability without retransmissions, which is suitable for delay-sensitive real-time video streaming applications \cite{JuFJ09,LuSW08,CHRL15}. With APP-FEC, well-designed redundant packets are transmitted along with data packets. By receiving enough subset of data and redundant packets, all of the original data packets can be recovered \cite{JuFJ09}. The correction capability becomes higher with more redundant packets in a coding block. In mobile surveillance networks, each mobile node (moving camera) is allocated certain amounts of wireless resource for video encoding and APP-FEC encoding. Nevertheless, the number of transmitted packets is limited by the total available system bandwidth. With higher/lower source encoding rate, the video analysis performance becomes better/worse with the cost of lower/higher APP-FEC protection capability. Therefore, a QoC-driven joint source coding and APP-FEC rate allocation scheme is proposed in this paper. Instead of considering human perception in traditional video streaming design, the proposed scheme optimizes the human detection performance at the cloud server when multiple mobile nodes compete for the limited wireless resource and upload vidoes via WWAN with a total data rate constraint. The proposed scheme can be formulated as a convex optimization problem \cite{BoVa04} and can be solved by convex optimization toolbox such as CVX \cite{CVX}. To the best of our knowledge, there is no QoC-driven work conducted when both video compressions and wireless transmission errors are considered.

@@

\textit{Notations:} The list of symbols used in this paper is summarized in Table \ref{Table: notations}.
\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{List of symbols}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{0.45 in}|p{2.5 in}|}
\hline
\textbf{Symbol} & \textbf{Definition}  \\
\hline
$q$ & \text{Quantization parameter (QP)} \\ \hline
$P\left(\cdot\right)$ & Human detection accuracy model \\ \hline
$n$ & Application layer forward error correction (APP-FEC) block size \\ \hline
$k$ & Number of source packets in an APP-FEC block \\ \hline
$t$ & Correction capability of an APP-FEC block \\ \hline
$\epsilon$ & Reception overhead efficiency of APP-FEC \\ \hline
$p$ & Probability of packet loss \\ \hline
$f\left(\cdot\right)$ & APP-FEC block correction rate \\ \hline
$\Phi\left(\cdot\right)$ & Cumulative distribution function of the standard Gaussian distribution \\ \hline
$M$ & Total number of mobile nodes in the system \\ \hline
$T^{\left(\text{GoP}\right)}$ & Group of pictures (GoP) time period \\
$S$ & Packet size \\ \hline
$N_m$ & Number of detected people in the view of the mobile node $m$ \\ \hline
$R^{\left(\text{T}\right)}$ & Total data rate target of the system \\ \hline
$R^{\left(\min\right)}$ & Minimum data rate requirement of each mobile node \\ \hline
$\mathbb{N}$ & Set of nature numbers \\ \hline
$c_m^{\left(1\right)}, c_m^{\left(2\right)}$ & Parameters in QP-rate model of the mobile node $m$ \\ \hline
$r_m^{\left(\text{S}\right)}$ & Source coding rate target of the mobile node $m$ \\ \hline
$r_m^{\left(\text{B}\right)}$ & Transmission data rate target of the mobile node $m$ \\ \hline
$c_m^{\left(3\right)}$, $c_m^{\left(4\right)}$ & Parameters in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$d_m\left(\cdot\right)$ & Distortion measured by the MSE in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$P^{\left(\text{req}\right)}$ & FEC block correction rate requirement of the MSE-driven rate allocation scheme in the control group. \\

@@

\begin{figure}[t]
%\vspace{-.2in}
\centering{\includegraphics[width=3.5 in]{Fig/GOP_FEC.pdf}}
\caption{GoP-level APP-FEC encoding \cite{WSHZ13}.}
\label{fig:GOP_FEC}
\end{figure}
\section{Scenarios and System Structure}
In a mobile surveillance network, multiple mobile nodes are randomly distributed and moving around in the area with different pedestrain densities as illustrated in Fig. \ref{fig:scenario}. Each mobile node can capture, encode and upload videos via a WWAN to a cloud server for video analyses such as human detection. The proposed system structure is shown in Fig. \ref{fig:system}. The captured camera view of each node is encoded with the high efficiency video coding (HEVC) \cite{SOHW12} encoder with different encoding data rates. The parameter estimation module determines the necessary parameters required by the cloud server. The encoded video packets and corresponding parameter packets of a single group of pictures (GoP) is then fed into the APP-FEC encoder, which generates certain amount of redundant packets and forms an APP-FEC block \cite{WSHZ13,BaTO08}. The concept of GoP-level APP-FEC encoding is shown in Fig. \ref{fig:GOP_FEC}. The cloud server receives the transmitted APP-FEC block with some packet lost due to either wireless transmission errors or network congestions. In this paper, the packet loss rate of each mobile node is assumed to be perfectly known by standard real-time protocol (RTP) and real-time control protocol (RTCP) \cite{Perk03,CHWY15}. The APP-FEC decoder decodes the APP-FEC block and fed the video packets to the video decoder. If the number of packet loss is higher than the correction capability of the APP-FEC block, the whole block is then dropped. The video decoder can conceal the lost video frames by copying the last successfully decoded video frame. After decoding the video, an object detection module performs the human detections and sends the detection results (content information) to the rate allocation module. Since the pedestrain densitie is different in the view of each mobile node, the human detection result (content information) is therefore different. Based on the content information and the necessary parameters delivered by the mobile nodes, the rate allocation module jointly optimizes the source coding rate and the APP-FEC coding rate for each mobile node under a pre-determined total data rate constraint, which is assumed to be affordable by the wireless network. The rate allocation result is then fed back to the mobile nodes for encoding and transmission process in the next iteration. Note that the rate allocation results are targets for the mobile nodes and the actural source coding and APP-FEC rates can be slightly different to the targets.

@@

Figure \ref{fig:accuracy} shows the human detection accuracy with respect to different video encoding qualities in terms of the QPs. Six video clips in the ETHZ dataset \cite{ELSG08} are encoded by the HEVC encoder \cite{X265} with $11$ different QPs from $15$ to $45$. The detection results of each video frame is compared with the ground-truth labels provided in the ETHZ dataset. An object is considered as correct detection if the overlapped area of the detection result and the corresponding ground-truth is larger than $50$ percent of the ground-truth area \cite{FGMR10}. Obviously, the detection accuracy is increasing as the video quality is increasing (i.e., the QP is decreasing). But the rate of increasing becomes small when the video quality is high enough since the artifact created by video compression is negligible. By adopting curve-fitting, the human detection accuracy model as a function of QP (i.e., $q$) can be approximated as:
\begin{equation}\label{eq:accuracy_model}
P\left(q\right) = -0.0098\cdot 2^{0.1206\cdot q}+0.6049.
\end{equation}
The solid line in Fig. \ref{fig:accuracy} is based on Eq. \eqref{eq:accuracy_model}. The root mean square error (RMSE) of the curve-fitting in Fig. \ref{fig:accuracy} is $1.104\%$.

@@

\section{APP-FEC and Block Correction Rate}
APP-FEC can provide reliable end-to-end streaming applications with packet level protection \cite{LuSW08}. Suppose a source block with $k$ packets is encoded into an APP-FEC block consisting $n \left(n\geq k\right)$ packets by adding $n-k$ redundant packets, an ideal APP-FEC decoder can reconstruct the original $k$ source packets from any $k$ out of $n$ received packets \cite{LuSW08} with correction capability $t=n-k$. The Reed-Solomon (RS) code, which operates on non-binary symbols, is a well-known APP-FEC scheme with ideal correction capability. However, the block size of RS code is constrained by the symbol size, which limits the flexibility of parameter selections in practice. For instance, considering the most commonly used RS code with $8$ bits per symbol, the total number of packets in an APP-FEC block is constrained by $255$, i.e., $k\leq n \leq 255$. Furthermore, the non-binary operations of the RS code cause high computational complexity in software \cite{LuSW08}. Such drawbacks make the RS code unattractive to high definition (HD) video streaming applications. With the development of APP-FEC, more practical schemes have been introduced. One of the attractive APP-FEC solutions for HD video streaming services is the Raptor code \cite{Shok06}, which has flexible parameters selection and linear decoding cost. Unlike the RS code, the correction capability of a Raptor code is unideal, given by $t=n-\left(1+\epsilon\right)k$, where $\epsilon$ is reception overhead efficiency. Nevertheless, the reception overhead efficiency of standardized Raptor code is very low and close to ideal correction capability \cite{LuSW08}. In this paper, the APP-FEC scheme with ideal correction capabiity is assumed for simplicity.

An APP-FEC block can be successfully decoded if the number of packet loss/error is not more than the correction capability $t$. If the packet losses are independent and identical distributed (\textit{i.i.d.}), the block correction rate (BCR) of an $\left(n,k\right)$ ideal APP-FEC code is given by a cumulative distribution function (CDF) of a Binomial distribution \cite{HHWL12}:
\begin{equation} \label{eq:BCR}
f=\sum_{j=0}^{t}\binom{n}{j}p^j\left(1-p\right)^{n-j},
\end{equation}
where $p$ is the packet loss rate. When $n$ is sufficiently large, $np\gg1$ and $n\left(1-p\right)\gg1$, the CDF of a Binomial distribution can be approximated by a CDF of Gaussian distribution with mean $np$ and variance $np\left(1-p\right)$ \cite{StWo11}. Therefore, Eq. \eqref{eq:BCR} can be approximated as:
\begin{equation} \label{eq:BCR_appx1}
f\approx \Phi\left(\frac{t-np}{\sqrt{np\left(1-p\right)}}\right)-\Phi\left(\frac{-np}{\sqrt{np\left(1-p\right)}}\right),
\end{equation}
where $\Phi\left(\cdot\right)$ is the CDF of the Gaussian distribution with $0$ mean and unit variance. If $np$ is large enough, The second term in Eq. \eqref{eq:BCR_appx1} is approximately $0$. And the BCR in Eq. \eqref{eq:BCR} can be further approximated as:
\begin{equation}\label{eq: BCR_appx_final}
f\approx \Phi\left(\frac{n-k-np}{\sqrt{np\left(1-p\right)}}\right)=\Phi\left(\frac{\sqrt{n}\left(1-p\right)-\frac{k}{\sqrt{n}}}{\sqrt{p\left(1-p\right)}}\right).
\end{equation}
When the APP-FEC block is formed every GoP time period (e.g., $0.5 - 1$ second), the APP-FEC block size $n$ is normally large enough with the available data rate to transmit HD videos in modern wireless network (e.g., 10 Mbps) and a reasonable packet size (e.g., $600$ bytes). With a typical packet loss rate in wireless networks without any other protection or retransmission schemes (e.g., $0.1 \% - 2 \%$), the approximation in Eq. \eqref{eq: BCR_appx_final} is valid.

>>>>

\everymath{\displaystyle}
\newcommand{\tab}[1]{\hspace{.02\textwidth}\rlap{#1}}
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Quality-of-Content (QoC)-based Joint Source and Channel Coding for Human Detections in A Mobile Surveillance Cloud
}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Xiang Chen, Jenq-Neng Hwang, De Meng, Kuan-Hui Lee, Ricardo L. de Queiroz}   \\
\thanks{This study is partially supported by the “103-EC-17-A-03-S1-214” project from the Ministry of Economic Affairs (MOEA) of Taiwan and “Advanced Wireless Broadband System and Inter-networking Application Technology Development Project” of the Institute for Information Industry which is subsidized by the Ministry of Economy Affairs of Taiwan.}
\thanks{Xiang Chen is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: xchen28@uw.edu).}% <-this % stops a space
\thanks{Jenq-Neng Hwang is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: hwang@uw.edu).}% <-this % stops a space
\thanks{De Meng is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA.}% <-this % stops a space
\thanks{Kuan-Hui Lee is with the Department
of Electrical Engineering, University of Washington, Seattle,
WA, 98195 USA (e-mail: ykhlee@uw.edu).}
\thanks{Ricardo L. de Queiroz is with the Department
of Computer Science, Universidade de Brasilia, Brasilia, Brazil (e-mail: queiroz@ieee.org).}

@@

\begin{abstract}
%\boldmath
More than 70 percent of all the consumer mobile Internet traffic will be mobile video transmissions in 2019. The development of wireless video transmission technologies have been boosted by the rapidly increasing demand of video streaming applications. Although more and more videos are delivered for video analytics purposes (e.g., object detection/tracking and action recognition, etc.), most of existing wireless video transmission schemes are developed to optimize human perception qualities, and are no longer optimal for video analyses.  In mobile surveillance networks, a cloud server collects videos from multiple moving cameras and detects suspicious people in all the camera views. Due to the mobility of the moving cameras such as smartphone or dash cameras, videos have to be uploaded through bandwidth-limited and error-prone wireless networks, which may cause quality degradation of the decoded videos and jeopardize the performance of video analyses. In this paper, we propose an effective rate allocation scheme for multiple moving cameras so that the human detection (content) performance can be improved. Therefore, the optimization criterion of the proposed rate allocation scheme is driven by quality-of-content (QoC). Both video source coding and application layer forward error correction (APP-FEC) coding rates are jointly optimized. Moreover, the proposed rate allocation problem is formulated as a convex optimization problem and can be efficiently solved by standard solvers. Plenty of simulations with the high efficient video coding (HEVC) encoded video sequences and the deformable part model (DPM) object detector demonstrate the effectiveness and favorable performance of our proposed QoC-driven scheme under different pedestrain densities and wireless conditions.

@@

The exponentially increasing demand of video streaming services has boosted the developement of wireless video transmission technologies \cite{Hwan09}. In most of the existing studies, the optimization targets for wireless video delivery are either quality-of-service (QoS) \cite{Hwan09,EhHa12,KPKG15} or quality-of-experience (QoE) \cite{CHLC15,CHWL14,CDHR15,SHJE13,YaFA15}. For QoS-based design, the transmission scheme is optimized for network parameters such as packet loss rate, delay, jitter, etc. For QoE-based design, QoS measures are mapped to users' perception and experience of decoded videos so that video transmission parameters can be adjusted to improve users' satisfaction \cite{FiHT10}. Both subjective and objective video quality measures can be applied to quantify the QoE-based system design \cite{MSSB10}.

The Internet of Things (IoT) becomes a novel paradigm in modern wireless telecommunications \cite{AtIM10}. And video-based IoT, which integrates image processing, computer vision and network frameworks, will help develop a new challenging scientific research area at the intersection of video and network technologies \cite{GBMP13}. Such research areas include surveillance system, automatic behavior analysis and event detection, etc. \cite{GBMP13}. In fact, more and more videos are transmitted for video analytics purposes rather than human perceptions. In \cite{LeHC15}, a vehicle tracking system with static surveillance cameras is developed. In \cite{ChHw14}, an unsupervised learning of camera link models for tracking humans across nonoverlapping static cameras is invented. Based on human detectors, pedestrian tracking systems in single moving cameras are proposed \cite{LHOP14,HWLH15}. A system of on-road pedestrian tracking across multiple moving cameras is studied in \cite{LeHw15}. Due to the large computational cost of video analyses applications and the inter-cooperating properties between multiple cameras, videos are required to be uploaded to a cloud server through wired and/or wireless networks. However, transmitting videos based on QoS or QoE based on existing designs are no longer optimal if the videos are delivered for video analyses. Therefore, it is necessary to develope more efficient video transmission schemes specifically for video analyses and computer vision applications.

Mobile surveillance network with multiple moving cameras, which have more flexible camera views comparing to traditional surveillance systems with static closed circuit television (CCTV), is introduced for better crime investigations and tragedy prevention \cite{LeHw15}. In mobile surveillance systems, videos are recorded by driving recorders (dash cameras) or smartphone cameras, and uploaded to remote cloud servers for further automatic video analyses. Due to the mobility nature of moving cameras, wireless wide area networks (WWAN) have to be used for video transmissions. Therefore, efficient video compressions, error protections and resource allocations are needed because of the bandwidth-limited and the error-prone natures of wireless networks.

In mobile surveillance networks, in order to recognize and track suspicious people, several video analytics technologies need to be applied such as human detection, human tracking, action recognition, behavior understanding, etc.. Among these technologies, human detection is the first step and the performances of other human-related video analytics applications are critically affected by the human detection results \cite{LeHw15}. Although plenty of work has been conducted to improve the object detector in computer vision field \cite{DaTr05,LeLS08,FGMR10}, few studies can be found in wireless video transmission area when the performance degradations caused by video compression, wireless transmission errors are considered. In \cite{MiBR13}, a saliency-based rate control system for human detection with a single camera is proposed. To improve the human detection accuracy, this scheme adaptively adjusts the quantization parameters (QPs) to preserve regions with small contrast from excessive smoothing based on a properly designed saliency map. In \cite{GCCC11,ReCT12}, image/video features instead of the full video sequences are uploaded to the cloud servers for video analyses. Although transmitting features can save lots of wireless resources, they are not suitable for surveillance purposes since the full video sequences are requried to be archived in the server for future investigations. In \cite{CHLQ15}, we proposed a video source encoding rate allocation scheme when multiple moving cameras compete for a limited amount of wireless resource. This scheme adequately allocate the wireless resource to each moving camera based on its previous human detection results (contents). Since the optimization objective is to improve human detection performance, this scheme is called a quality-of-content (QoC)-based design.

In this paper, we extend our previous work in \cite{CHLQ15} by considering packet losses in wireless networks. Among several techniques of improving the reliability of data transmissions, we adopte the application layer forward error correction (APP-FEC) code since it can provide certain correction capability without retransmissions, which is suitable for delay-sensitive real-time video streaming applications \cite{JuFJ09,LuSW08,CHRL15}. With APP-FEC, well-designed redundant packets are transmitted along with data packets. By receiving enough subset of data and redundant packets, all of the original data packets can be recovered \cite{JuFJ09}. The correction capability becomes higher with more redundant packets in a coding block. In mobile surveillance networks, each mobile node (moving camera) is allocated certain amounts of wireless resource for video encoding and APP-FEC encoding. Nevertheless, the number of transmitted packets is limited by the total available data rate. With higher/lower source encoding rate, the video analysis performance becomes better/worse with the cost of weeker/stronger APP-FEC protection. Therefore, a QoC-driven joint source coding and APP-FEC rate allocation scheme is proposed in this paper. Instead of considering human perception in traditional video streaming design, the proposed scheme optimizes the human detection performance at the cloud server when multiple mobile nodes compete for the limited wireless resource and upload vidoes via WWAN with a total data rate constraint. The proposed scheme can be formulated as a convex optimization problem \cite{BoVa04} and can be solved by convex optimization toolbox such as CVX \cite{CVX}. To the best of our knowledge, there is no QoC-driven work conducted when both video compressions and wireless transmission errors are considered.

@@

\textit{Notations:} The list of symbols used in this paper is summarized in Table \ref{Table: notations}.
\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{List of symbols}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{0.45 in}|p{2.5 in}|}
\hline
\textbf{Symbol} & \textbf{Definition}  \\
\hline
$q$ & \text{Quantization parameter (QP)} \\ \hline
$P\left(\cdot\right)$ & Human detection accuracy model \\ \hline
$n$ & Application layer forward error correction (APP-FEC) block size \\ \hline
$k$ & Number of source packets in an APP-FEC block \\ \hline
$t$ & Correction capability of an APP-FEC block \\ \hline
$\epsilon$ & Reception overhead efficiency of APP-FEC \\ \hline
$p$ & Probability of packet loss \\ \hline
$f\left(\cdot\right)$ & APP-FEC block correction rate \\ \hline
$\Phi\left(\cdot\right)$ & Cumulative distribution function of the standard Gaussian distribution \\ \hline
$M$ & Total number of mobile nodes in the system \\ \hline
$T^{\left(\text{GoP}\right)}$ & Group of pictures (GoP) time period \\ \hline
$S$ & Packet size \\ \hline
$N_m$ & Number of detected people in the view of the mobile node $m$ \\ \hline
$R^{\left(\text{T}\right)}$ & Total data rate target of the system \\ \hline
$R^{\left(\min\right)}$ & Minimum data rate requirement of each mobile node \\ \hline
$\mathbb{N}$ & Set of nature numbers \\ \hline
$c_m^{\left(1\right)}, c_m^{\left(2\right)}$ & Parameters in QP-rate model of the mobile node $m$ \\ \hline
$r_m^{\left(\text{S}\right)}$ & Source coding rate target of the mobile node $m$ \\ \hline
$r_m^{\left(\text{B}\right)}$ & Transmission data rate target of the mobile node $m$ \\ \hline
$c_m^{\left(3\right)}$, $c_m^{\left(4\right)}$ & Parameters in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$d_m\left(\cdot\right)$ & Distortion measured by the MSE in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$P^{\left(\text{req}\right)}$ & FEC block correction rate requirement of the MSE-driven rate allocation scheme in the control group. \\

@@

\begin{figure}[t]
%\vspace{-.2in}
\centering{\includegraphics[width=3.5 in]{Fig/GOP_FEC.pdf}}
\caption{GoP-level APP-FEC encoding \cite{WSHZ13}.}
\label{fig:GOP_FEC}
\end{figure}
\section{Scenarios and System Structure}
In a mobile surveillance network, multiple mobile nodes are randomly distributed and moving around in the area with different pedestrain densities as illustrated in Fig. \ref{fig:scenario}. Each mobile node can capture, encode and upload videos via a WWAN to a cloud server for video analyses such as human detection. The proposed system structure is shown in Fig. \ref{fig:system}. The captured camera view of each node is encoded with the high efficiency video coding (HEVC) \cite{SOHW12} encoder with different encoding data rates. The parameter estimation module determines the necessary parameters required by the cloud server. The encoded video packets and corresponding parameter packets of a single group of pictures (GoP) is then fed into the APP-FEC encoder, which generates certain amount of redundant packets and forms an APP-FEC block \cite{WSHZ13,BaTO08}. The concept of GoP-level APP-FEC encoding is shown in Fig. \ref{fig:GOP_FEC}. The cloud server receives the transmitted APP-FEC block with some packet lost due to either wireless transmission errors or network congestions. In this paper, the packet loss rate of each mobile node is assumed to be perfectly known by standard real-time protocol (RTP) and real-time control protocol (RTCP) \cite{Perk03,CHWY15}. The APP-FEC decoder decodes the APP-FEC block and fed the video packets to the video decoder. The undecodable video frames are dropped. The video decoder can conceal the lost video frames by copying the last successfully decoded video frame. After decoding the video, an object detection module performs the human detections and sends the detection results (content information) to the rate allocation module. Since the pedestrain density is different in the view of each mobile node, the human detection result (content information) is therefore different. Based on the content information and the necessary parameters delivered by the mobile nodes, the rate allocation module jointly optimizes the source coding rate and the APP-FEC coding rate for each mobile node under a pre-determined total data rate constraint, which is assumed to be affordable by the wireless network. The rate allocation result is then fed back to the mobile nodes for encoding and transmission process in the next iteration. Note that the rate allocation results are targets for the mobile nodes and the actural source coding and APP-FEC rates can be slightly different to the targets.

@@

Figure \ref{fig:accuracy} shows the human detection accuracy with respect to different video encoding qualities in terms of the QPs. Six video clips in the ETHZ dataset \cite{ELSG08} are encoded by the HEVC encoder \cite{X265} with $11$ different QPs from $15$ to $45$. The detection results of each video frame is compared with the ground-truth labels provided in the ETHZ dataset. An object is considered as correct detection if the overlapped area of the detection result and the corresponding ground-truth is larger than $50$ percent of the ground-truth area \cite{FGMR10}. Obviously, the detection accuracy is increasing as the video quality is increasing (i.e., the QP is decreasing). But the rate of increasing becomes small when the video quality is high enough since the artifacts created by video compression are negligible. By adopting curve-fitting, the human detection accuracy model as a function of QP (i.e., $q$) can be approximated as:
\begin{equation}\label{eq:accuracy_model}
P\left(q\right) = -0.0098\cdot 2^{0.1206\cdot q}+0.6049.
\end{equation}
The solid line in Fig. \ref{fig:accuracy} is based on Eq. \eqref{eq:accuracy_model}. The root mean square error (RMSE) of the curve-fitting in Fig. \ref{fig:accuracy} is $1.104\%$.

@@

\section{APP-FEC and Block Correction Rate}
APP-FEC can provide reliable end-to-end streaming applications with packet level protection \cite{LuSW08}. Suppose a source block with $k$ packets is encoded into an APP-FEC block consisting $n \left(n\geq k\right)$ packets by adding $n-k$ redundant packets, an ideal APP-FEC code, with correction capability $t=n-k$, can reconstruct the original $k$ source packets from any $k$ out of $n$ received packets \cite{LuSW08}. The Reed-Solomon (RS) code, which operates on non-binary symbols, is a well-known APP-FEC scheme with ideal correction capability. However, the block size of the RS code is constrained by the symbol size, which limits the flexibility of parameter selections in practice. For instance, considering the most commonly used RS code with $8$ bits per symbol, the total number of packets in an APP-FEC block is constrained by $255$, i.e., $k\leq n \leq 255$. Furthermore, the non-binary operations of the RS code cause high computational complexity in software \cite{LuSW08}. Such drawbacks make the RS code unattractive to high definition (HD) video streaming applications. With the development of APP-FEC, more practical schemes have been introduced. One of the attractive APP-FEC solutions for HD video streaming services is the Raptor code \cite{ShAm06}, which has flexible parameters selection and linear decoding cost. Unlike the RS code, the correction capability of the Raptor code is unideal, given by $t=n-\left(1+\epsilon\right)k$, where $\epsilon$ is reception overhead efficiency. Nevertheless, the reception overhead efficiency of standardized Raptor code is very low and close to ideal correction capability \cite{LuSW08}. In this paper, the APP-FEC scheme with ideal correction capabiity is assumed.

An APP-FEC block can be successfully decoded if the number of packet loss/error is not more than the correction capability $t$. If the packet losses are independent and identical distributed (\textit{i.i.d.}), the block correction rate (BCR) of an $\left(n,k\right)$ ideal APP-FEC code is given by a cumulative distribution function (CDF) of a Binomial distribution \cite{HHWL12}:
\begin{equation} \label{eq:BCR}
f=\sum_{j=0}^{t}\binom{n}{j}p^j\left(1-p\right)^{n-j},
\end{equation}
where $p$ is the packet loss rate. When $n$ is sufficiently large, $np\gg1$ and $n\left(1-p\right)\gg1$, the CDF of a Binomial distribution can be approximated by a CDF of Gaussian distribution with mean $np$ and variance $np\left(1-p\right)$ \cite{StWo11}. Therefore, Eq. \eqref{eq:BCR} can be approximated as:
\begin{equation} \label{eq:BCR_appx1}
f\approx \Phi\left(\frac{t-np}{\sqrt{np\left(1-p\right)}}\right)-\Phi\left(\frac{-np}{\sqrt{np\left(1-p\right)}}\right),
\end{equation}
where $\Phi\left(\cdot\right)$ is the CDF of the Gaussian distribution with $0$ mean and unit variance. If $n\cdot p$ is large enough, The second term in Eq. \eqref{eq:BCR_appx1} is approximately $0$. And the BCR in Eq. \eqref{eq:BCR} can be further approximated as:
\begin{equation}\label{eq: BCR_appx_final}
f\approx \Phi\left(\frac{n-k-np}{\sqrt{np\left(1-p\right)}}\right)=\Phi\left(\frac{\sqrt{n}\left(1-p\right)-\frac{k}{\sqrt{n}}}{\sqrt{p\left(1-p\right)}}\right).
\end{equation}
When the APP-FEC block is formed every GoP time period (e.g., $0.5 - 1$ second), the APP-FEC block size $n$ is normally large enough with the available data rate to transmit HD videos in modern wireless network (e.g., 10 Mbps) and a reasonable packet size (e.g., $600$ bytes). With a typical packet loss rate in wireless networks without any other protection or retransmission schemes (e.g., $0.1 \% - 2 \%$), the approximation in Eq. \eqref{eq: BCR_appx_final} is valid.
